Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-29 awipev-CO2.Rmd
added chunk availability of data

>>>>

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
selected_nydata_minute <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_minute.rds")) %>%
  dplyr::select(ends_with("_qf")) #%>%
s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_raw_qf)
s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
qflags <- tibble(pco2_corr = s1,
                 sal_fb = s2,
                 sal_insitu_ctd = s3,
                 temp_dur = s4,
                 temp_fb = s5,
                 temp_insitu_11m = s6,
                 phINT = s7,
                 phEXT = s8)

  summarise_all(percentcumsum)
  dplyr::mutate_all(funs("percent"= cumsum(.)/100))
p <-  ggplot(data = selected_nydata_minute) +
  geom_bar(aes(x = as.factor(pco2_corr_qf)))
p
rm(selected_nydata_minute)
```
